Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-11-17 paper/answer_reviewers.tex

\documentclass[letterpaper, 12pt]{article}

\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage[lmargin=1 in, rmargin=1 in, tmargin=1 in, bmargin=1 in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{times}
\usepackage{xcolor}

\begin{document}

\textbf{Reviewer 1}

\bigskip

\textit{My main comment concerns the bias in the observation of S minus P times. The authors measure the observed lag time from the centroid of the cross-correlation function within the time window 2 seconds before and after the theoretical lag time if the tremor source was on the plate boundary (L330-335). I understand that such kind of constraint is sometimes useful for obtaining realistic solutions, but I am worried whether this constraint works for too strong bias that concentrates all tremor depths to the plate boundary depths. In other words, the S minus P time measurements should be free from theoretical time lags when discussing the spatial relationship between tremor and plate boundary. How about using the whole time window or focusing on the window around the maximum peak? In any case, the authors should check and show that these time window limitations do not strongly affect the results.}

\bigskip

To be more precise, when we plot the cross-correlation of the horizontal-to-vertical components, we see a primary peak around time lag 0, and a secondary peak around time lag 4-5 s, corresponding to the time lag between the P-wave and the S-wave. To be sure to pick the secondary peak and not the main one, we first look for a local maximum close to the theoretical time lag. Once we have found the secondary peak, we select a time window around this peak to do the clustering, and compute the moment centroid. The width of the time window selected to compute the moment centroid may have an effect on the estimation of the depth of the tremor. To verify this, we varied the width of the time window and computed the corresponding variations of the depth of the tremor. We added this precision in the text.

\bigskip

\textit{Thickness or depth extent of tremor sources in this study is derived from the scattering of time lags or depths for one-minute-long time windows (L414-438). However, none of the time lag or depth distribution for one-minute-long time windows are presented in the manuscript. I recommend showing at least some examples of these distributions. Besides, I am not (and probably most readers would not be) familiar with Qn estimator. Please give a more detailed explanation about what Qn estimator is and in which case it works well (compared with MAD).}

\bigskip

We added an example of distribution of time lags in the supplement. We added a description of the Qn estimator and its advantage compared to the MAD in the text.

\bigskip

\textit{L194: Ghosh et al., 2010 -> Ghosh et al., 2010ab?}

\textit{L306: Ghosh et al., 2010 -> Ghosh et al., 2010b?}

\bigskip

We modified the reference.

\bigskip

\textit{L330: I cannot get the meaning of the sentence, "We considered only the horizontal component with the maximum value of the peak". Do you select the EW or NS components with the larger maximum value of the peak?}

\bigskip

Yes, we select the component (EW or NS) that has the largest maximum value of the peak. We modified this sentence in the text.

\bigskip

\textit{L346-358: half width is a typical measure for uncertainties when picking a peak value. In this case, when picking a centroid value, it is more natural to use standard deviation or MAD (or Qn?).}

\bigskip

Here we wanted to make the distinction between a sharp peak and a flatter peak which could have the same moment centroid. This is why we choose the half-width.

\bigskip

\textit{L375: different different -> different}

\bigskip

We corrected this sentence.

\bigskip

\textit{L468-474: I think this paragraph is not an important conclusion of this work and is already placed in the Discussion just above the Conclusion. No need to repeat here.}

\bigskip

We deleted this paragraph.

\bigskip

\textit{Figure 6, Figure 8, Figure 11, Figure 12: Please consider changing the symbol of Three Bumps (triangles). They are the same symbol as the array positions in Figure 1 and are a bit confusing.}

\bigskip

We modified the symbols for Three Bumps.

\bigskip

\textbf{Reviewer 2}

\bigskip

\textit{I have only one minor quibble: in lines 443 - 445 the authors state "The depth range of the tremor is larger than the depth range of the low-frequency earthquakes, but this may be due to the uncertainty of the determination of the tremor depth." As far as I can tell, the depth range of members of an LFE family was not measured by Chestler and Creager (2017). Their three models assume a planar structure. A recent JGR paper by Sammis and Bostock (2021) proposed that LFEs beneath Vancouver Island occur at the sites of granular jams in a flow channel between 0.5 and 1.5 kilometers thick. So, the assumption of a planar distribution of LFEs in a family may be premature.}

\bigskip

There are two papers by Chestler and Creager in 2017. We added the reference in the text. Here, we are considering the range over all LFE families of the distance between the location of the LFE family and the plate boundary, not the depth range of the source of the LFEs within a single LFE family. The LFE families are close to the plate boundary, but not exactly on a plane. We modified the text and we added the comparison with the thickness of the flow channel.

\end{document}

### 2021-11-17 paper/agujournaltemplate_highlighted.tex

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

@@

Moreover, the zone with high low Poisson's ratio observed by ~\citeA{HYN_2015} has a large vertical extent (about 10 kilometers). If the whole zone is associated with quartz deposition and tectonic tremor generation, we should also observe a large vertical distribution of the source of the tremor. ~\citeA{KAO_2006} have used a Source Scanning Algorithm to detect and locate tremor, and have indeed located tremor in the continental crust, with a wide depth range of over 40 km. They noted that this wide depth range could not arise from either analysis uncertainties or a systematic bias in the velocity model they used. Uncertainties on the location of the tremor have been estimated by  ~\citeA{IDE_2012} at about 1.5 km in epicenter and 4.5 km in depth. A follow-up study by ~\citeA{KAO_2009} gave a thickness of the tremor zone of 5-10 km. This depth range is inconsistent with the depth of the LFEs, which have been located on a thin band at or near the plate interface with a rupture mechanism that corresponds to the thrust dip angle ~\cite{IDE_2007_GRL}. In the Olympic Peninsula, LFE families have been identified and located by ~\citeA{CHE_2017_JGR}, and all LFE families were located near the plate interface. Further study is thus needed to narrow the uncertainty on the depth of the source of the tremor, and verify whether tremor occurs in a wider zone than LFEs. \\

@@

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/BS_-05_-05_PWS_PWS_cluster_ccwin.eps}
\caption{Envelopes of the stacked cross-correlation functions ordered by time for the Big Skidder array for the 110 one-minute long time windows when tremor was detected in a 5 km by 5 km grid cell located 7 kilometers southwest of the array. Top shows time windows (black) that fit the stack well. Bottom shows time windows (blue) that do not fit the stack well. Left panel is the cross-correlation of the EW component with the vertical component, and right panel is the cross-correlation of the NS component with the vertical component. The cross-correlation functions have been cut between 2 and 8 seconds to focus on the time lags around the peaks.}
\label{pngfiguresample}
\end{figure}

@@

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. For this cross-correlation, we keep only the values of lag times $\tau$ between one second before and one second after the time of the maximum of the absolute value of the stack $S_i (\tau)$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

We considered only the horizontal component with the maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the theoretical time lag if the source of the tremor was located on the plate boundary. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. We did the same analysis for the eight arrays of the experiment. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/uncertainty_PWS_PWS.eps}
\caption{Map of the uncertainty on the depth of the tremor based on the width of the stack of the envelopes of the cross-correlation functions for arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

In the following, we kept only the data points for which the maximum amplitude of the stack is higher than 0.05. Figures 6 and 7 show respectively a map and three cross-sections of the depth of the source of the tremor. Figure 8 shows a map of the distance between the source of the tremor and the plate boundary from the Preston model, alongside with the depth of the low-frequency earthquake families observed by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}. There is a good agreement between the depth of the source of the tremor, the depth of the low-frequency earthquake families, and the depth of the plate boundary. On the cross-section figures, we compare the distance of the source of the tremor to the plate boundary for different locations of the cross-section. We note that the depth of the tremor matches well the depth of the low-frequency earthquakes. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/depth_PWS_PWS.eps}
\caption{Map of the depth of the source of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}. The three black lines indicate the positions of the cross-sections shown in Figure 7. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles)}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=5cm, trim={4.5cm 0.5cm 6cm 0cm},clip, angle=270]{figures/section_strike_PWS_PWS.eps}
\caption{Cross-sections showing depth of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR} for cross sections A-A' , B-B', and C-C' shown in Figure 6. The black line corresponds to the plate boundary profile of McCrory (2006) along the southern most black line shown on Figure 6, and the dashed line to the plate boundary profile of Preston (2003). The color bar shows the distance of the tremor and the low-frequency earthquakes along the strike. Only tremor and low-frequency earthquakes less than 10 km away from the profile line are shown. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/d_to_pb_PWS_PWS_P.eps}
\caption{Map of the distance between the plate boundary (from the Preston model) of the tremor and of the low-frequency earthquake families (filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}). Tremor located below the plate boundary is blue, and above is red. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

@@

Previous studies have shown evidence for seismic anisotropy near the slab interface ~\cite{NIK_2009} and in the overriding continental crust ~\cite{CAS_1996}. If the source of the tremor is located in or under the anisotropic layer, the time lag between the arrival of the direct P-wave and the arrival of the direct S-wave could be different different depending on whether we consider the East-West component or the North-South component. To verify whether possible anisotropy could affect our results, we computed the time difference between the timing of the maximum of the stack of the envelopes of the stacked cross-correlation functions between the East-West component and the vertical component, and between the North-South component and the vertical component. We also computed the associated difference in depth of the source of the tremor (see Figure 9) for all arrays and all locations of the tremor. The difference in time is generally less than 0.25 s while the difference in depth is generally less than 2 kilometers, which is similar to the uncertainty on the tremor depth. As the time difference between the East-West component and the North-South component due to anisotropy is expected to vary depending on the relative position of the array compared to the source of the tremor, we also plotted the time difference as a function of the distance from source to array, and as a function of the azimuth, as well as the corresponding depth difference (Figure 9). The time difference does not increase with the distance from the source to the array, and there is no seismic path orientation that gives bigger time difference. Thus, seismic anisotropy does not seem to have a significant effect on the time lags between the arrival of the direct P-wave and the arrival of the direct S-wave, and can be neglected. ~\citeA{NIK_2009} observed anisotropy in the low-velocity layer beneath station GNW, located in the eastern Olympic Peninsula, south of the eight seismic arrays used in this study. If the tremor is located above the low-velocity layer, we do not expect this source of seismic anisotropy to introduce a significant effect on our measured time lags. ~\citeA{NIK_2009} locate the low-velocity layer above the plate boundary, in the lower continental crust, which is shallower than the location given by ~\citeA{BOS_2013}, who locates the low-velocity layer in the upper oceanic crust. However, even if a low-velocity layer with 5 \% anisotropy is located in the lower continental crust as indicated by ~\citeA{NIK_2009}, the resulting difference in time lags should not be more than a few tenths of a second, and the resulting difference in depth should not be more than 2 kilometers. ~\citeA{CAS_1996} observed anisotropy in the continental crust, especially in the upper 20 kilometers to the north of our arrays. However, the anisotropy resulted in time delays of the seismic waves of no more than 0.32s for deep earthquakes (40-60 km depth) and not more than 0.20s for shallow earthquakes (15-30 km depth). The corresponding difference in tremor depth is similar to the uncertainty. \\

@@

As proposed by ~\citeA{KAO_2009}, the source of the tremor could be distributed inside a layer that is 15 or more kilometers thick. We have assumed that all the tremor within a given grid cell originate from the same depth, and averaged over all the data to get the tremor depth. However, instead of being located on the same plane near the plate boundary, the tremor may be scattered over a layer surrounding the plate boundary. To compute the thickness of this layer, for each location of the array and the source of the tremor, we computed for each one-minute-long time window for which the cross-correlation function matches well the stacked cross-correlation the time lag between the time corresponding to the maximum absolute value for the cross-correlation function and the time corresponding to the maximum absolute value for the stacked cross-correlation. We thus obtained a distribution of time lags and the corresponding distribution of depths, and we tried to estimate the scale of the interval over which the depths vary. Using the standard deviation could lead to overestimate the width of the interval, and the corresponding thickness of the tremor layer, as the standard deviation is very sensitive to outliers. Instead, we use the Qn estimator of ~\citeA{ROU_1993}, which is a more robust estimator of scale, similar to the median absolute deviation. We then used the scale of the interval over which the tremor depth varies as an estimate of the thickness of the tremor layer (see Figure 11). The average thickness of the tremor zone is about 1.6 km, while nearly all the values of the thickness are less than 3km, which is substantially lower than the depth extent from ~\citeA{KAO_2009}. The smallest values for the thickness are about 0.8-2 kilometers. \\

>>>>

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

@@

Moreover, the zone with high low Poisson's ratio observed by ~\citeA{HYN_2015} has a large vertical extent (about 10 kilometers). If the whole zone is associated with quartz deposition and tectonic tremor generation, we should also observe a large vertical distribution of the source of the tremor. ~\citeA{KAO_2006} have used a Source Scanning Algorithm to detect and locate tremor, and have indeed located tremor in the continental crust, with a wide depth range of over 40 km. They noted that this wide depth range could not arise from either analysis uncertainties or a systematic bias in the velocity model they used. Uncertainties on the location of the tremor have been estimated by  ~\citeA{IDE_2012} at about 1.5 km in epicenter and 4.5 km in depth. A follow-up study by ~\citeA{KAO_2009} gave a thickness of the tremor zone of 5-10 km. This depth range is inconsistent with the depth of the LFEs, which have been located on a thin band at or near the plate interface with a rupture mechanism that corresponds to the thrust dip angle ~\cite{IDE_2007_GRL}. In the Olympic Peninsula, LFE families have been identified and located by ~\citeA{CHE_2017_JGR,CHE_2017_G3}, and all LFE families were located near the plate interface. Further study is thus needed to narrow the uncertainty on the depth of the source of the tremor, and verify whether tremor occurs in a wider zone than LFEs. \\

@@

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. \textbf{For all time windows, there is a primary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at $\tau = 0 s$ (not shown in the Figure). Additionally, for about 40\% of the time windows, we also see a secondary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at about $\tau = 4.5 s$.} As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/BS_-05_-05_PWS_PWS_cluster_ccwin.eps}
\caption{Envelopes of the stacked cross-correlation functions for the Big Skidder array for the 110 one-minute long time windows when tremor was detected in a 5 km by 5 km grid cell located 7 kilometers southwest of the array. Top shows time windows (black) that fit the stack well. Bottom shows time windows (blue) that do not fit the stack well. Left panel is the cross-correlation of the EW component with the vertical component, and right panel is the cross-correlation of the NS component with the vertical component. The cross-correlation functions have been cut between 2 and 8 seconds to focus on the time lags around the peaks.}
\label{pngfiguresample}
\end{figure}

@@

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. \textbf{We only want to verify whether the waveform $S_{i j} (\tau)$ around the secondary peak matches well with the stack $S_i (\tau)$. We thus look for the maximum of the absolute value of the stack $S_i (\tau)$ between one second before and one second after the theoretical time lag between P- and S-wave arrival if the source was on the plate boundary. We call the time lag corresponding to this maximum $\tau_{max}$. Then for the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$}, we keep only the values of lag times $\tau$ between one second before and one second after \textbf{$\tau_{max}$}. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value \textbf{$S_{i j} (\tau_{max})$} to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

\textbf{To compute the depth, we select the EW or the NS component with the larger maximum value of the peak.} We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the \textbf{time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier}. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. \textbf{To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054.} We did the same analysis for the eight arrays of the experiment. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/uncertainty_PWS_PWS.eps}
\caption{Map of the uncertainty on the depth of the tremor based on the width of the stack of the envelopes of the cross-correlation functions for arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

In the following, we kept only the data points for which the maximum amplitude of the stack is higher than 0.05. Figures 6 and 7 show respectively a map and three cross-sections of the depth of the source of the tremor. Figure 8 shows a map of the distance between the source of the tremor and the plate boundary from the Preston model, alongside with the depth of the low-frequency earthquake families observed by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3}. There is a good agreement between the depth of the source of the tremor, the depth of the low-frequency earthquake families, and the depth of the plate boundary. On the cross-section figures, we compare the distance of the source of the tremor to the plate boundary for different locations of the cross-section. We note that the depth of the tremor matches well the depth of the low-frequency earthquakes. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/depth_PWS_PWS.eps}
\caption{Map of the depth of the source of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3}. The three black lines indicate the positions of the cross-sections shown in Figure 7. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons)}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=5cm, trim={4.5cm 0.5cm 6cm 0cm},clip, angle=270]{figures/section_strike_PWS_PWS.eps}
\caption{Cross-sections showing depth of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3} for cross sections A-A' , B-B', and C-C' shown in Figure 6. The black line corresponds to the plate boundary profile of McCrory (2006) along the southern most black line shown on Figure 6, and the dashed line to the plate boundary profile of Preston (2003). The color bar shows the distance of the tremor and the low-frequency earthquakes along the strike. Only tremor and low-frequency earthquakes less than 10 km away from the profile line are shown. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/d_to_pb_PWS_PWS_P.eps}
\caption{Map of the distance between the plate boundary (from the Preston model) of the tremor and of the low-frequency earthquake families (filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3}). Tremor located below the plate boundary is blue, and above is red. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

@@

Previous studies have shown evidence for seismic anisotropy near the slab interface ~\cite{NIK_2009} and in the overriding continental crust ~\cite{CAS_1996}. If the source of the tremor is located in or under the anisotropic layer, the time lag between the arrival of the direct P-wave and the arrival of the direct S-wave could be different depending on whether we consider the East-West component or the North-South component. To verify whether possible anisotropy could affect our results, we computed the time difference between the timing of the maximum of the stack of the envelopes of the stacked cross-correlation functions between the East-West component and the vertical component, and between the North-South component and the vertical component. We also computed the associated difference in depth of the source of the tremor (see Figure 9) for all arrays and all locations of the tremor. The difference in time is generally less than 0.25 s while the difference in depth is generally less than 2 kilometers, which is similar to the uncertainty on the tremor depth. As the time difference between the East-West component and the North-South component due to anisotropy is expected to vary depending on the relative position of the array compared to the source of the tremor, we also plotted the time difference as a function of the distance from source to array, and as a function of the azimuth, as well as the corresponding depth difference (Figure 9). The time difference does not increase with the distance from the source to the array, and there is no seismic path orientation that gives bigger time difference. Thus, seismic anisotropy does not seem to have a significant effect on the time lags between the arrival of the direct P-wave and the arrival of the direct S-wave, and can be neglected. ~\citeA{NIK_2009} observed anisotropy in the low-velocity layer beneath station GNW, located in the eastern Olympic Peninsula, south of the eight seismic arrays used in this study. If the tremor is located above the low-velocity layer, we do not expect this source of seismic anisotropy to introduce a significant effect on our measured time lags. ~\citeA{NIK_2009} locate the low-velocity layer above the plate boundary, in the lower continental crust, which is shallower than the location given by ~\citeA{BOS_2013}, who locates the low-velocity layer in the upper oceanic crust. However, even if a low-velocity layer with 5 \% anisotropy is located in the lower continental crust as indicated by ~\citeA{NIK_2009}, the resulting difference in time lags should not be more than a few tenths of a second, and the resulting difference in depth should not be more than 2 kilometers. ~\citeA{CAS_1996} observed anisotropy in the continental crust, especially in the upper 20 kilometers to the north of our arrays. However, the anisotropy resulted in time delays of the seismic waves of no more than 0.32s for deep earthquakes (40-60 km depth) and not more than 0.20s for shallow earthquakes (15-30 km depth). The corresponding difference in tremor depth is similar to the uncertainty. \\

@@

As proposed by ~\citeA{KAO_2009}, the source of the tremor could be distributed inside a layer that is 15 or more kilometers thick. We have assumed that all the tremor within a given grid cell originate from the same depth, and averaged over all the data to get the tremor depth. However, instead of being located on the same plane near the plate boundary, the tremor may be scattered over a layer surrounding the plate boundary. To compute the thickness of this layer, for each location of the array and the source of the tremor, we computed for each one-minute-long time window for which the cross-correlation function matches well the stacked cross-correlation the time lag between the time corresponding to the maximum absolute value for the cross-correlation function and the time corresponding to the maximum absolute value for the stacked cross-correlation. We thus obtained a distribution of time lags and the corresponding distribution of depths, and we tried to estimate the scale of the interval over which the depths vary. \textbf{An example of time lags distribution is shown in Figure S8 of the supplementary material.} Using the standard deviation could lead to overestimate the width of the interval, and the corresponding thickness of the tremor layer, as the standard deviation is very sensitive to outliers. Instead, we use the Qn estimator of ~\citeA{ROU_1993}, which is a more robust estimator of scale, similar to the median absolute deviation (MAD). \textbf{Qn is equal to the $k$th order statistic of the $\begin{pmatrix} n \\ 2 \end{pmatrix}$ interpoint distances where $n$ is the number of points, and $k = \begin{pmatrix} h \\ 2 \end{pmatrix}$ with $h = \left[ \frac{n}{2} \right] + 1$ and $\left[ x \right]$ denote the integer part of $x$. As the MAD, the Qn estimator is not very sensitive to outliers, and it has the advantage of being suitable for asymmetric distributions, contrary to the MAD, which attaches equal importance to positive and negative deviations from the median.} We then used the scale of the interval over which the tremor depth varies as an estimate of the thickness of the tremor layer (see Figure 11). The average thickness of the tremor zone is about 1.6 km, while nearly all the values of the thickness are less than 3km, which is substantially lower than the depth extent from ~\citeA{KAO_2009}. The smallest values for the thickness are about 0.8-2 kilometers. \\
